\documentclass[11pt,a4paper,oneside]{report}

% MARK - Packages
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage[x11names,table,xcdraw]{xcolor}
\usepackage{natbib}
\usepackage{mathrsfs}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\usepackage[scr]{rsfso}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{bigfoot}
\usepackage[numbered,framed]{matlab-prettifier}
\usepackage{titletoc,tocloft}
\usepackage{setspace}
\usepackage{natbib}
\usepackage[a4paper,left=2cm,right=2cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage[siunitx]{circuitikz}
\usepackage{framed}
\usepackage{quoting}
\usepackage{xlop}
\usepackage{float}
\usepackage{titlesec}
\usepackage{csvsimple}
\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[numbered,framed]{matlab-prettifier}
\usepackage{physics} % for 'pdv' macro
\usepackage{multicol}
\usepackage{courier}
\usepackage{sourcecodepro}
\usepackage[normalem]{ulem}
\usepackage{pgfplots}
\usepackage[bookmarks]{hyperref}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{url}
\usepackage{import}
\useunder{\uline}{\ul}{}

% MARK - Metadata
\author{
  Jesse Onolememen\\
  20344056
  \and
  Omar Issa\\
  19204747
  \and
  David Jones\\
  20329631
}
\title{
  \textbf{EEEN30150 Modelling \& Simulation} \\
  \large Minor Project 2 (MP2): Dynamic Equations}
\date{\today}
\onehalfspacing
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{3}
\graphicspath{../exports}
\bibliographystyle{agsm}
\numberwithin{equation}{section}
\setlength{\parindent}{0pt}

% MARK - Quotations
\colorlet{shadecolor}{LavenderBlush2}
\colorlet{framecolor}{lightgray}
\renewenvironment{shaded*}{%
  \def\FrameCommand{\setlength{\FrameRule}{2pt}\fboxsep=\FrameSep \fcolorbox{framecolor}{shadecolor}}%
  \MakeFramed {\advance\hsize-\width \FrameRestore}}%
 {\endMakeFramed}


\newenvironment{shquote}
 {\begin{shaded*}
  \quoting[leftmargin=0pt, vskip=0pt]
 }
 {\endquoting
 \end{shaded*}
}

% Title format
\titleformat{\chapter}[display]
  {\normalfont\bfseries}{}{0pt}{\Huge}
\titlespacing*{\chapter}{0pt}{0pt}{12pt}

% MARK - Custom Commands
\setcounter{section}{0}
\renewcommand{\thesection}{\arabic{section}}
\newcommand{\lpt}[1]{\mathcal{L}\{#1\}}
\newcommand{\sbracket}[1]{\left[#1 \right]}
\newcommand{\bracket}[1]{\left(#1 \right)}

\def\therefore{\boldsymbol{\text{ }
\leavevmode
\lower0.4ex\hbox{$\cdot$}
\kern-.5em\raise0.7ex\hbox{$\cdot$}
\kern-0.55em\lower0.4ex\hbox{$\cdot$}
\thinspace\text{ }}}

% Listings
\lstset{style=Matlab-editor}
%\setmonofont{Lucida Console}[Scale=MatchLowercase] % select a suitable monospaced font
\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}
\lstset{framextopmargin=50pt,frame=bottomline}

\usepackage{xcolor}
\definecolor{maroon}{cmyk}{0, 0.87, 0.68, 0.32}
\definecolor{halfgray}{gray}{0.55}
\definecolor{ipython_frame}{RGB}{207, 207, 207}
\definecolor{ipython_bg}{RGB}{247, 247, 247}
\definecolor{ipython_red}{RGB}{186, 33, 33}
\definecolor{ipython_green}{RGB}{0, 128, 0}
\definecolor{ipython_cyan}{RGB}{64, 128, 128}
\definecolor{ipython_purple}{RGB}{170, 34, 255}


%%
%% Python definition (c) 1998 Michael Weber
%% Additional definitions (2013) Alexis Dimitriadis
%% modified by me (should not have empty lines)
%%
\lstdefinelanguage{MatLab}{
    basicstyle=\footnotesize,
    keywordstyle=\color{ipython_green}\ttfamily,
}

% Matrix columns
\setcounter{MaxMatrixCols}{15}
\newcommand{\nodecirc}[1]{\textcircled{#1} \hspace{0.15cm} \triangleright \hspace{0.25cm}}

% MARK - Begin Document

\begin{document}

% S; Front Page
\maketitle

% S; Plagarism Declaration
\include{frontmatter/Plagarism}

% S; Table of Contents
\newpage
\setlength{\cftsubsecindent}{1.5cm}
\setlength{\cftsubsubsecindent}{1.5cm}
\doublespacing
\tableofcontents
\onehalfspacing

% S; Sections
\include{frontmatter/Abstract}
\include{sections/J_DeviceModelling}
\include{sections/J_CircuitModelling}
\include{sections/NumericalAnalysis}
\include{sections/Simulation}
\include{sections/Visualisation}

% S; Appendix
\include{frontmatter/Appendix}

Collaborative Approach for Enhanced Efficiency and Quality

In our project, we adopted a collaborative group approach, recognizing the benefits of collective brainstorming and problem-solving for each sub-problem. Rather than working individually and waiting for one team member to complete their section before moving on, we leveraged the power of teamwork to foster efficiency and produce higher-quality outcomes.

By working together, we harnessed the diverse perspectives, knowledge, and skills of each team member. This collaborative environment allowed us to generate a range of innovative solutions, benefiting from the collective wisdom and expertise of the group. Through active participation and open communication, we fostered a productive atmosphere where ideas were shared, refined, and built upon collaboratively.

It is important to emphasize that the work we have presented is a culmination of our joint efforts as a team. The report and video presentation are the result of our collaborative endeavors, where each member contributed their expertise and insights. By pooling our strengths and working collaboratively, we were able to achieve a higher level of quality and create a more comprehensive output than what could have been accomplished individually.

Our collaborative approach not only facilitated efficient problem-solving but also enhanced the overall quality of our work. By leveraging the collective intelligence of the team, we were able to explore different perspectives, validate ideas, and produce a well-rounded project that reflects the synergy of our collaborative efforts.

% S; Biblography
\bibliography{frontmatter/references}

\end{document}













